---
title: "Homework 6"
author: "JR Chansakul"
date: 2020-12-09
output: github_document
  
---

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```


### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}

## Clean Data for Regression Analysis
birthweight_df = 
  read_csv("./data/birthweight.csv", na = c("", "NA", "Unknown")) %>%
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex), 
         malform = as.factor(malform),
         frace = as.factor(frace), 
         mrace = as.factor(mrace),
         babysex = recode(babysex, 
                          "1" = "Male", 
                          "2" = "Female"),
         frace = recode (frace,
                         "1" = "White", 
                         "2" = "Black", 
                         "3" = "Asian", 
                         "4" = "Puerto Rican",
                         "8" = "Other",
                         "9" = "Unknown"),
         malform = recode(malform, 
                          "0" = "absent",
                          "1" = "present"),
         mrace = recode(mrace,
                        "1" = "White", 
                        "2" = "Black", 
                        "3" = "Asian", 
                        "4" = "Puerto Rican", 
                        "8" = "Other"))
            
##Check for missing values - None 
sum(!complete.cases(birthweight_df))

## Check distributions and variable typles 
birthweight_df %>%
  skimr::skim()

```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}

## Full Model 
full_model = lm(bwt ~ ., data = birthweight_df)

## Backward Stepwise Regression Method  
step(full_model, direction = "backward") 
step(full_model, direction = "backward")[["terms"]]

## Fitted Model 
fitted_model1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)

summary(fitted_model1)

## Plot of model residuals against fitted values

birthweight_df %>% 
  modelr::add_residuals(fitted_model1) %>%
  modelr::add_predictions(fitted_model1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.2) +
  geom_hline(yintercept = 0, color = "blue")

  labs(
    x = "Fitted Values",
    y = "Residuals",
    title = "Residuals against fitted values") +
  theme(plot.title = element_text(hjust = 0.5))
```

 
Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}

## Simple Model
model2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)

## Interaction Model
model3 = lm(bwt ~ (bhead + blength + babysex)^3, birthweight_df)

```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}

## Cross Validation comparison 
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    fitted_model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model3 = map(train, ~lm(bwt ~ (bhead + blength + babysex)^3, data = .x))) %>% 
  mutate(
    rmse_mod1 = map2_dbl(fitted_model1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_mod3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))

##RMSE Comparisons

cv_df %>%
  select(starts_with("rmse")) %>% 
  unnest() %>% 
  gather(key = "model", value = "rmse") %>% 
  mutate(model = 
           str_replace(model, "rmse_", "")) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin(aes(fill = model)) + 
  labs(title = "RMSE Comparison") +
  theme(plot.title = element_text(hjust = 0.5))
```

